Data 621---HW1---Regression Model---Version 2

### 2020-09-08 HW1/RegModel_Adler.Rmd
Imputation, center/scaling, start commentary on results of c/s

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r loadPackages}
library(corrplot)
library(RColorBrewer)
library(ggplot2)
library(scales)
library(data.table)
```

@@

```{r missingTable}
missingObs <- MBmelt[, .(Missing = sum(is.na(Value)),
                         Percentage = sum(is.na(Value)) / length(Value)),
                     keyby = Metric][Missing > 0][order(-Missing)]
knitr::kable(missingObs, digits = 3L)
```

@@

statTable <- MBmelt[, .(Min = min(Value, na.rm = TRUE),
                        Q1 = quantile(Value, 0.25, na.rm = TRUE),
                        Median = median(Value, na.rm = TRUE),
                        Q3 = round(quantile(Value, 0.75, na.rm = TRUE)),
                        Max = max(Value, na.rm = TRUE),
                        Mean = mean(Value, na.rm = TRUE),
                        StDev = sd(Value, na.rm = TRUE),
                        IQR = IQR(Value, na.rm = TRUE)), keyby = Metric]
knitr::kable(statTable, digits = 2L)
```

@@

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r loadPackages}
library(caret)
library(corrplot)
library(RColorBrewer)
library(ggplot2)
library(scales)
library(data.table)
```

@@

```{r missingTable}
missingObs <- MBmelt[, .(Missing = sum(is.na(Value)),
                         Percentage = sum(is.na(Value)) / length(Value)),
                     keyby = Metric][Missing > 0][order(-Missing)]
knitr::kable(missingObs, digits = 3L,
caption = 'Training Data with Missing Observations')
```

@@

statTable <- MBmelt[, .(Min = min(Value, na.rm = TRUE),
                        Q1 = quantile(Value, 0.25, na.rm = TRUE),
                        Median = median(Value, na.rm = TRUE),
                        Q3 = round(quantile(Value, 0.75, na.rm = TRUE)),
                        Max = max(Value, na.rm = TRUE),
                        Mean = mean(Value, na.rm = TRUE),
                        StDev = sd(Value, na.rm = TRUE),
                        IQR = IQR(Value, na.rm = TRUE)), keyby = Metric]
knitr::kable(statTable, digits = 2L,
             caption = 'Training Data Summary Statistics')
```

@@

# Data Preperation
## Task
Describe how you have transformed the data by changing the original variables or
creating new variables. If you did transform the data or create new variables,
discuss why you did this. Here are some possible transformations:

  a. Fix missing values (maybe with a Mean or Median value)
  b. Create flags to suggest if a variable was missing
  c. Transform data by putting it into buckets
  d. Mathematical transforms such as log or square root(or use Box-Cox)
  e. Combine variables (such as ratios or adding or multiplying) to create new
  variables

## Analysis
The `caret` package for R is the gold-standard catch-all interface for machine
learning techniques for those not using the tidyverse. Otherwise, the same
author's `tidymodels` package may be used as well. When using `caret`, almost
all of the following imputation and transformation is done as pre-processing
to the model. For the purposes of this homework, they are being performed
manually to demonstrate understanding.

### Imputation
Since we are restricting ourselves to the world of the simple linear regression
model, it makes sense to use a Z-transformation to standardize the models.
Prior to this, the missing variables should be imputed. Looking at the summary
statistics table, the median is not that far off of the mean in most cases with
the exceptions of `TEAM_BASERUN_SB` and `TEAM_BATTING_SO`. Therefore, for an
initial imputation, we will use the mean so that the overall mean is unaffected
for the Z-transform. This **will** artificially reduce the SD, however. We could
address that by calculating the mean and SD, *prior* to imputation. We will not
do so now for simplicity.

```{r imputeMean}
MBmelt[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
```

### Transformations
The first transform applied will be centering and scaling, as discussed above.

```{r centerScale}
MBmelt[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
```

At this point we would hope to see Gaussian-looking densities.
```{r plotScaled}
ggplot(MBmelt, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free')
```

Some of the variables, like `TEAM_BATTING_2B` or `TEAM_BATTING_SO` show
Gaussian-like behavior, with some allowances for the discrete nature of the
input data (those wiggles at the crest of `TEAM_BATTING_SO` for example). Others
are classic right tailed (exponential/gamma-esque) such as `TEAM_FIELDING_E` or
`TEAM_BATTING_3B`. Still others are clearly multimodal. Then there are the
weird spike-like ones as well.

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
